Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-25 WSSSPE3/report/wg_appendix_funding_spec_expert.tex
Appendix H:  A few changes.

The UK allows this kind of collaboration to support the creation of scientific
software for the large supercomputing resource (ARCHER). However, while the
support can come the staff of the Edinburgh Parallel Computing Centre,
who host the computer, this ``embedded CSE'' resource also funds the
programming coming from local groups. This has been very helpful in providing
funding to establish local groups. These work best when these groups develop good
collaborations with national cyberinfrastructure pools. When an organization
assembles a developer pool, diversity is developed and skills can be
transferred.

@@

The CANARIE group (Canada) accepts proposals for providing services to broad
communities, integrating people who are doing things that are complementary. The
goal is to make the available stack more robust and richer for everyone. They
offer short cycles of funding that can have use creating some useful
functionality that shows a diversity of input and draws from across disciplines as a key metric,  If this metric is met successfully, 
then more funding may follow. This can apply within or across institutions.

@@

In this respect, information gathering via a survey and subsequent analysis could be
very useful. We would need to assemble a list of targeted individuals. (what
positions and ranks are likely to know and care enough to respond?) Perhaps the
Science Gateway Institute has already acquired information that could be helpful
to advance this issue, and/or craft a proper survey and suggest target individuals.

>>>>

The UK allows this kind of collaboration to support the creation of scientific
software for the large supercomputing resource (ARCHER). However, while the
support can come from the staff of the Edinburgh Parallel Computing Centre,
who hosts the computer, this ``embedded CSE'' resource also funds the
programming coming from local groups. This has been very helpful in providing
funding to establish local groups. It works best when these groups develop good
collaborations with national cyberinfrastructure pools. When an organization
assembles a developer pool, diversity is developed and skills can be
transferred.

@@

The CANARIE group (Canada) accepts proposals for providing services to broad
communities, integrating people who are doing things that are complementary. The
goal is to make the available stack more robust and richer for everyone. They
offer short cycles of funding for creating some useful
functionality that shows a diversity of input and draws from across disciplines as a key metric,  If this metric is met successfully, 
then more funding may follow. This can apply within or across institutions.

@@

In this respect, information gathering via a survey and subsequent analysis could be
very useful. We would need to assemble a list of targeted individuals. (What
positions and ranks are likely to know and care enough to respond?) Perhaps the
Science Gateway Institute has already acquired information that could be helpful
to advance this issue, and/or craft a proper survey and suggest target individuals.
